---
title: "PS #01"
format: html

---

## Problem 1 - Wine data

### a.

First, import the data from `wine.data` to the `wine_df`

```{r}
wine_df <- read.csv("~/桌面/Stats-506/PS-01/wine.data",header=FALSE)
```

Then, give appropriate column names to the `wine_df`

```{r}
colnames(wine_df) <- c('class','Alcohol','Malic acid','Ash','Alcalinity of ash','Magnesium','Total phenols','Flavanoids','Nonflavanoid phenols',
'Proanthocyanins','Color intensity','Hue','OD280/OD315 of diluted wines','Proline')
```

This shows the first 10 rows of the `wine_df`:

```{r}
#| echo: false
wine_df[1:10,]
```

### b.

Next, check the number of wines within each class:

```{r}
table(wine_df$class)
```

This is exactly the same as in `wine.names`

### c.

The wine with the highest alcohol content belongs to class 1:

```{r}
wine_df[which.max(wine_df$Alcohol),]$class
```

The wine with the highest alcohol content belongs to class 2:

```{r}
wine_df[which.min(wine_df$Alcohol),]$class
```

  26 wines have higher levels of magnesium than 114 mg/l of magnesium:

```{r}
sum(wine_df$Magnesium>114)
```

15 class one, 6 class two and 5 class three have higher levels of magnesium than average German beer:

```{r}
table(wine_df[which(wine_df$Magnesium>114),]$class)
```