---
title: "PS #04"
author: Boyuan Ma
github: https://github.com/mab0y/Stats-506/tree/main/PS-04
format: 
  html:
    embed-resources: true
toc: true
---
[Link to GitHub](https://github.com/mab0y/Stats-506/tree/main/PS-04) 

I have provided hyperlinks to all pertinent resources and references that assisted me in addressing this problem.

## Problem 1 - Tidyverse
### a.
Import the libraries and save data it to the environment:
```{r}
#| include = FALSE
library(tidyverse)
```

```{r}
library(nycflights13)

airlines_data <- airlines
airports_data <- airports
flights_data <- flights
planes_data <- planes
weather_data <- weather
```

Use [`left_join`](https://stackoverflow.com/questions/1299871/how-to-join-merge-data-frames-inner-outer-left-right) to merge `flights` and `airports` by `origin` and `faa`:
```{r}
flights_data_origin <- flights_data %>% left_join(airports_data, by = c("origin" = "faa"))
```

Group flights by airport name and calculate the mean and median departure delay per airport:
```{r}
flights_data_origin_summary <- flights_data_origin %>%
  group_by(name) %>%
  summarize(mean_dep_delay = mean(dep_delay, na.rm = TRUE), median_dep_delay = median(dep_delay, na.rm = TRUE)) %>%
  filter(!is.na(name)) %>%
  arrange(desc(mean_dep_delay))%>%
  ungroup()
```

```{r}
#| echo: false
print(flights_data_origin_summary,n=Inf)
```

Repeat the steps for `dest` and `faa`:
```{r}
flights_data_dest <- flights_data %>% left_join(airports_data, by = c("dest" = "faa"))
```
[Count](https://stackoverflow.com/questions/22767893/count-number-of-rows-by-group-using-dplyr
) the rows of each group and exclude any destination with under 10 flights:
```{r}
flights_data_dest_summary <- flights_data_dest %>%
  group_by(name) %>%
  summarize(mean_arr_delay = mean(arr_delay, na.rm = TRUE), median_arr_delay = median(arr_delay, na.rm = TRUE), n_row = n()) %>%
  filter(n_row>=10& !is.na(name)) %>%
  arrange(desc(mean_arr_delay))%>%
  select(-n_row)%>%
  ungroup()
```

```{r}
#| echo: false
print(flights_data_dest_summary,n=Inf)
```

b.
Merge `flights` and `planes` by `tailnum`:
```{r}
flights_data_model <- flights_data %>% left_join(planes, by = "tailnum")
```
Calculate average speed for each model:
```{r}
flights_data_model_summary <- flights_data_model %>%
  group_by(model) %>%
  summarize(average_speed=mean(distance/(air_time/60)), count=n())%>%
  filter(!is.na(model)) %>%
  arrange(desc(average_speed)) %>%
  ungroup() %>%
  head(1)
```

```{r}
#| echo: false
print(flights_data_model_summary,n=Inf)
```